---
title: "Reproducible Research: Peer Assessment 1"
output: 
html_document:
keep_md: true
---
# Loading and preprocessing the data

1. Unzip and Read the Data
Code for reading in the dataset and/or processing the data
No further analysis is required in this stage
```{r} 
data <- read.csv(unz("activity.zip", "activity.csv"))
```

2. Histogram of the total number of steps taken each day
```{r} 
## Calc steps Per Day and remove NA
stepsPerDay <- tapply(data$steps,data$date,sum,na.rm = TRUE)

## Create histogram

par(mfrow=c(1,1))
hist(stepsPerDay,20)
```


## What is mean total number of steps taken per day?

3. Mean and median number of steps taken each day
```{r} 
## Calc mean per day and remove NA
meanStepsPerDay <- mean(stepsPerDay)
print(meanStepsPerDay)

## Calc median per day and remove NA
medianStepsPerDay <- median(stepsPerDay)
print(medianStepsPerDay)
```

## What is the average daily activity pattern?
4. Time series plot of the average number of steps taken
```{r} 
## 4. Time series plot of the average number of steps taken
meanStepPerInterval <- tapply(data$steps,data$interval,mean,na.rm = TRUE)
plot(as.numeric( names(meanStepPerInterval)),meanStepPerInterval)
```

5. The 5-minute interval that, on average, contains the maximum number of steps
```{r} 
print(max(meanStepPerInterval))
```


## Imputing missing values
6. Code to describe and show a strategy for imputing missing data: we use na.rm = TRUE.
7. Histogram of the total number of steps taken each day after missing values are imputed
```{r} 
stepsPerDay <- tapply(data$steps,data$date,sum,na.rm = TRUE)
hist(stepsPerDay,20)
```


## Are there differences in activity patterns between weekdays and weekends?

8. Panel plot comparing the average number of steps taken per 
   5-minute interval across weekdays and weekends
```{r}
day <- weekdays(as.Date(data$date,'%Y-%m-%d'))
weekendDays <- (day=="Sunday" | day=="Saturday")
meanStepPerIntervalWeekend <- tapply(data[weekendDays,]$steps,data[weekendDays,]$interval,mean,na.rm = TRUE)
meanStepPerIntervalWeekdays <- tapply(data[!weekendDays,]$steps,data[!weekendDays,]$interval,mean,na.rm = TRUE)

## Create Figures
par(mfrow=c(2,1))
plot(as.numeric( names(meanStepPerIntervalWeekend)),meanStepPerIntervalWeekend, main="umber of steps taken per 5-minute interval - weeends")
plot(as.numeric( names(meanStepPerIntervalWeekdays)),meanStepPerIntervalWeekdays, main="umber of steps taken per 5-minute interval - weekdays")
```

### Code for Running rmarkdown from consolue: *rmarkdown::render("PA1_template.Rmd")*.